Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Clarify why foil characteristics were normalized

Results from the XFOIL calculations for the airfoil profiles are shown in
Figure~\ref{fig:foil-Re-dep}, where values of the maximum lift coefficient
$C_{l_{\max}}$, minimum drag coefficient $C_{d_{\min}}$ and maximum
lift-to-drag ratio are normalized (for the comparison between foils) and plotted
\textit{versus} $Re_c$. In general, larger camber is associated with decreased foil
performance at lower Reynolds number. The data and processing code for these
calculations is available from \cite{Bachant2015-NACAXX20-XFOIL}.

>>>>

Results from the XFOIL calculations for the airfoil profiles are shown in
Figure~\ref{fig:foil-Re-dep}, where values of the maximum lift coefficient
$C_{l_{\max}}$, minimum drag coefficient $C_{d_{\min}}$, and maximum
lift-to-drag ratio are normalized (to visualize relative differences in scaling
between the foils) and plotted \textit{versus} $Re_c$. In general, larger camber
is associated with decreased foil performance at lower Reynolds number. The data
and processing code for these calculations is available from
\cite{Bachant2015-NACAXX20-XFOIL}.
